\section{Workload Distribution}\label{sec:workload-distribution}

We would like to refer to the milestones outlined in the initial report when explaining our workload distribution.

\begin{itemize}
    \setlength\itemsep{0em}
    \item \textbf{Project Setup}:
    The fundamental Java project setup including the Gradle build configurations were
    configured by Andreas.
    Additionally, Andreas built the CI pipeline to automate the tests and ensure the build integrity.
    We employed a PR-template to make pull request easier to draft and easier to review.
    \item \textbf{API}:
    Andreas has designed and implemented overall structures of the core networking layer,
    which are used by API and P2P connections.
    Chung Hwan implemented the serializing and deserializing methods for the API message formats.
    \item \textbf{P2P Protocol}:
    Andreas designed the handshake protocol and implemented it with including the definition of packet formats and handler logics.
    The business logic (implemented within the \ttt{GossipModule}) were implemented by Andreas.
    \item \textbf{Tests}:
    Chung Hwan wrote the in-memory test cases for the packet decoding and encoding.
    Andreas wrote the end-to-end test cases to ensure the network layer works as intended.
    \item \textbf{Documentation \& Reports}:
    Chung Hwan and Andreas co-worked writing the midterm report.
    Andreas updated its contents to form the endterm report.
\end{itemize}

\subsection{Individual efforts}\label{subsec:individual-efforts}

The overall git commit history provides an additional source for the individual workload distribution
in addition to the information outlined below.

\paragraph{Andreas:} Since the initial report, I have roughly spent 85 hours in total on the project.
This metric is provided by the time tracking tool of my IDE (code and reports).
It, therefore, doesn't account for time spent outside the
IDE  (e.g., time spent with research, lecture material or online material around the topic
or tools).

\paragraph{Chung Hwan:} I invested about 30 hours for this project after submitting the initial report.
Since this metric is calculated from commit history, it includes only the time the code was written.
