\section{Workload Distribution}\label{sec:workload-distribution}

We would refer to the milestones from the previous initial report to explain our workload distribution.

\begin{itemize}
    \setlength\itemsep{0em}
    \item \textbf{Project Setup}:
    Andreas has set up the Java project with the Gradle build configurations.
    Andreas also built the CI pipeline to automate the tests and ensure the build integrity.
    PR-template was written by Andreas, which helps to make pull requests easier.
    \item \textbf{API}:
    Andreas has designed and implemented overall structures of the core networking layer,
    which are used by API and P2P connections.
    Chung Hwan implemented the serializing and deserializing methods for the API message formats.
    \item \textbf{P2P Protocol}:
    Andreas designed the handshake protocol and implemented it with writing packet formats and handler classes.
    Andreas also designed the packet format and the handler logic, which is used for the notification system
    and is implemented in the Gossip module.
    \item \textbf{Tests}:
    Chung Hwan wrote the in-memory test cases for the packet decoding and encoding.
    Andreas wrote the end-to-end test cases to ensure the network layer works as intended.
    \item \textbf{Documentation \& Reports}:
    Chung Hwan and Andreas co-worked writing the midterm report.
\end{itemize}

\subsection{Individual efforts}\label{subsec:individual-efforts}

\paragraph{Andreas:} Since the initial report, I have roughly spent 55 hours in total on the project.
This metric is provided by the time tracking tool of my IDE (code and reports).
It, therefore, doesn't account for time spent outside the
IDE  (e.g., time spent with research, lecture material or online material around the topic
or tools).

\paragraph{Chung Hwan:} I invested about 30 hours for this project after submitting the initial report.
Since this metric is calculated from commit history, it includes only the time the code was written.

